---
title: "shrinkage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## shrinkage optimization

tried ntree = 500 and ntree = 5000, there is not much improvement but using 5000 is very time-consuming. So use ntree = 500 and optimize shinkage through out the process.

first, find the shrinkage in store 1
```{r }
library(readxl)
library(tree)
library(Metrics)
library(randomForest)
library(gbm)

# read file
Store = list()
set.seed(1)
Store[[1]] = read_excel("Store2-1.xlsx")
Store[[2]] = read_excel("Store3-1.xlsx")
Store[[3]] = read_excel("Store4-1.xlsx")
Store[[4]] = read_excel("Store5-1.xlsx")
Store[[5]] = read_excel("Store6-1.xlsx")
Store[[6]] = read_excel("Store7-1.xlsx")
Store[[7]] = read_excel("Store8-1.xlsx")
Store[[8]] = read_excel("Store9-1.xlsx")



```

```{r }
RMSE = list()
#best_shrink = list()
best_n = list()
S = 100
for (i in 6){
  print(i)
}
  
for (i in 8){
  train = (Store[[i]]$Random == 'Train')
  store_train = Store[[i]][train,]
  store_test = Store[[i]][!train,]
  y = data.frame(Store[[i]][99:122])
  y_train = data.frame(store_train[99:122])
  y_test = data.frame(store_test[99:122])

 
  # try 100 shrinkage
  shrink = c(1:S)
  boost.mse = c(1:S)
  boost.mse[1:S] = 0

  boost.store = list()
  pred.boost = c()
  s = c()
  
  
  for (j in 1:24){
    for (l in 1:S){
      set.seed(1)
      boost.store = gbm(y_train[,j]~.-Random,store_train,distribution = "gaussian", n.trees=1000,shrinkage=(l * (1/S)),interaction.depth=6)
      pred.boost = predict(boost.store,newdata=store_test,n.trees=1000)
      boost.mse[l] = rmse(y_test[,j], pred.boost)
}
    s[j] = shrink[boost.mse == min(boost.mse)]
    print(j)
    
}
  #print(i)
  
  best_shrink[[i]] = s
  
}

```
```{r}
for (i in 1:8){
  train = (Store[[i]]$Random == 'Train')
  store_train = Store[[i]][train,]
  store_test = Store[[i]][!train,]
  y = data.frame(Store[[i]][99:122])
  y_train = data.frame(store_train[99:122])
  y_test = data.frame(store_test[99:122])
  RMSE_boosted = c()
  N = c()
  number = c(1:100)
  boost.mse = c()
  
  for (j in 1:24){
     k = 1
    for (n in number){
      set.seed(1)
      boost.store = gbm(y_train[,j]~.-Random,store_train,distribution = "gaussian", n.trees=(n*100),shrinkage=(best_shrink[[i]][j]/100),interaction.depth=6)
      pred.boost = predict(boost.store,newdata=store_test,n.trees=(n*100))
      boost.mse[n] = rmse(y_test[,j], pred.boost)
      #k = k+1
}
    #N[j] = number[boost.mse == min(boost.mse)]
    RMSE_boosted[j] = min(boost.mse)
    print(j)
    print(RMSE_boosted)
}
  print(i)
  #best_n[[i]] = N
  RMSE[[i]] = RMSE_boosted
  
}
name = c('Store_1', 'Store_2',  'Store_3',  'Store_4',  'Store_5', 'Store_6', 'Store_7',  'Store_8')
number
names(RMSE) = paste(name)
write.csv(RMSE, "boosted_gm.csv", row.names=FALSE)
  
```
180.673301   1.887388  32.879792  65.771520   5.804888  53.809279  17.097518  54.153896  86.312446
[10]  51.058330  65.761221  73.752073 129.730672 129.737836  26.600013  25.437829  17.904442 175.713388
[19]  27.585116  53.117777 137.940631   3.000032  89.611827  31.567549




best_shrink = list(c(37,1,25,9,1,1,1,1,2,26,1,24,26,29,1,1,7,41,11,17,1,1 ,1 ,12),
                   c(4,1  ,3 ,28  ,1  ,2  ,1,  1, 19,  2,  2, 16,  1,  1, 37,  1,  1,  1,  1, 37, 22,  2,  1, 19),
                   c(28  ,6  ,1  ,1 , 1 ,54 ,29 , 1 ,40  ,1 , 1  ,1,  1 , 1 , 1 , 1 , 1 , 1 ,43 , 1  ,1, 38, 11 , 1),
                   c(1 , 7, 36 , 2 , 1,  1 , 1  ,1 , 1 , 2  ,1,  8  ,1, 52,  1 ,93 , 1 , 1,  1,  3, 13, 51 ,12,  1),
                   c(1,  5, 18  ,6 ,32, 27 , 7 , 9 , 1 , 2 ,26 , 1 , 1,  2 ,22,  1, 16,  9,  1,  9,  8,  9,  3,  2),
                   c(1, 27, 49  ,6 ,54  ,1 ,24, 26 ,35 ,14, 28  ,8,  1 , 1,  2, 93, 1 , 1, 1, 13, 25, 56, 5, 5),
                   c(24 ,51, 39, 39,  1 , 3, 13,  1 , 1,  5 ,58, 40,  1,  1,  1,  1, 12,  1,  1, 27, 20, 69, 33, 54),
                   c(44,1 ,2  ,1, 94, 26,  1,  1,  1,  6,  1,  1, 48, 73, 12,  1, 37,  2  ,2  ,1  ,1  ,1  ,1  ,7))

train = (Store[[1]]$Random == 'Train')
store_train = Store[[1]][train,]
store_test = Store[[1]][!train,]
y = data.frame(Store[[1]][99:122])
y_train = data.frame(store_train[99:122])
y_test = data.frame(store_test[99:122])
RMSE_boosted = c()
set.seed(1)
boost.store = gbm(y_train[,1]~.-Random,store_train,distribution = "gaussian", n.trees=500,shrinkage=(best_shrink[[1]][1]/100),interaction.depth=6)
pred.boost = predict(boost.store,newdata=store_test,n.trees=2500)
boost.mse[k] = rmse(y_test[,1], pred.boost)